---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

# unsound

Retrieve Current and Historical Upper Air Soundings Data from the University of Wyoming

## Description

The University of Wyoming maintains a server (<http://weather.uwyo.edu/upperair/sounding.html>) that provides an interface to query current and historical upper air soundings data. Tools are provided to query this service and retrieve the data.

Ref:

- <https://stackoverflow.com/questions/52535696/save-content-in-web-as-data-frame/52539658#52539658>
- <https://stackoverflow.com/questions/52543892/web-scraping-using-httr-give-xml-nodeset-error/52545775?noredirect=1#comment92066543_52545775>

## What's Inside The Tin

The following functions are implemented:

- `get_region_codes`:	Retrive region names and codes
- `get_sounding_data`:	Get sounding data for a station
- `rbind_soundings`:	Turn a list of soundings data frames into a single data frame

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/unsound")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(unsound)
library(magick)
library(tidyverse) # overkill since it's just for data frame pretty printing

# current verison
packageVersion("unsound")

```

### Region codes

```{r}
get_region_codes()
```

### Full example (via the SO question(s))

```{r cache=TRUE}
# get the start/end range
startDate <- as.Date("01-11-17", format="%d-%m-%y")
endDate <- as.Date("31-01-18",format="%d-%m-%y")

# make a sequence
days <- seq(startDate, endDate, "1 day")

lapply(days[1:4], function(day) {
  
  Sys.sleep(3) # be kind to their servers
  
  get_sounding_data(
    region = "seasia",
    date = day,
    from_hr = "00",
    to_hr = "00",
    station_number = "48657"
  )
}) -> soundings_48657

# Notice there's missing data for one day
str(soundings_48657)

# make one big data frame
soundings_48657 <- rbind_soundings(soundings_48657)

glimpse(soundings_48657)

soundings_48657
```

### Maps

```{r}
get_sounding_map(
  station_number = "48657", 
  date = Sys.Date()-1, 
  map_type = "skewt", 
  map_format = "gif", 
  region = "seasia", 
  from_hr = "00", 
  to_hr = "00"
)
```
